### 2012-05-21 docs/makefiles/makefiles.tex
add info about t/

The \boxlib\ build system separates the compiler-specific information
from the machine-specific information---this allows for reuse of the
compiler information.  The only machine-specific parts of the build system
are for the MPI library locations, contained in {\tt GMakeMPI.mak}.
The compiler flags for the various compilers are listed in the
files in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_mk/comps/}.

@@

\subsection{Core MAESTRO modules}

@@

@@

>>>>

The \boxlib\ build system separates the compiler-specific information
from the machine-specific information---this allows for reuse of the
compiler information.  The only machine-specific parts of the build system
are for the MPI library locations, contained in {\tt GMakeMPI.mak}.
The compiler flags for the various compilers are listed in the
files in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_mk/comps/}.  The compiler
is set via the {\tt COMP} variable in the problem's {\tt GNUmakefile}.

There are several options in addition to the compiler that affect the
build process: {\tt MPI}, {\tt OMP}, and {\tt NDEBUG}---these turn on/off
MPI parallelization, OpenMP parallelization, and debugging.  Together,
these choices along with the compiler name are reflected in the name
of the executable.

When the `{\tt make}' command is run, the object and module files are
written into a directory {\tt t/{\em OS}.{\em COMP}.{\em other}/},
where {\tt \em OS} is the operating system detected by the build
system, {\tt \em COMP} is the compiler used, and {\tt \em other}
reflects any other build options (MPI, OpenMP, debugging, etc.) used.
Separating each build into a separate subdirectory under the problem
directory allows for multiple builds of \maestro\ to exist
side-by-side in the problem directory.

@@

\subsection{Core \maestro\ modules}

@@

Typing `{\tt make clean}' deleted the object and module files for the
current build (i.e., the current choice of {\tt MPI}, {\tt NDEBUG},
{\tt COMP}, and {\tt OMP}).  This also removes any of the compile-time
generated source files.  Any other builds are left unchanged.

Typing `{\tt make realclean}' deletes the object and module files for
all builds---i.e., the entire {\tt t/} directory is removed.

@@

{\tt BOXLIB\_USE\_MPI\_WRAPPERS}
